Multi-fluids for Representing Sub-filter-scale Convection

### 2020-03-27 submit2/manuscript.tex
First submmitted version and empty revised version and responses to reviewer comments.
Hilary started working on revisions

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

@@

Slow progress has been made improving the parameterisation of sub-grid-scale
convection since \citeA{AS74}, \citeA{Tied89}, \citeA{GR90} and \citeA{KF90}. Convection is still
one of the weakest aspects of large scale models of the atmosphere
\cite{HPB+14,SAB+13,ipcc41}. Improvements have been made relaxing
the quasi-equilibrium assumption \cite{PR98,GG05,Par14}, including
stochasticity \cite{PC08} and allowing net mass transport by convection
\cite{KB08,MB19}. These developments have enabled limited simulation
in the grey zone, where convection is partially resolved. However
there are still systematic biases implying that improvements should
still be possible.

\citeA{TWV+18} proposed multi-fluid modelling of convection in order
to treat non-equilibrium and net mass transport correctly and consistently
with the same numerics and physics controlling thermals, the stable
environment and downdraught dynamics. \citeA{Yano14} derived similar
equations for multiple segments and showed how this is a generalisation
of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
diffusivity mass flux'' or extended EDMF scheme also uses similar
equations but \citeA{TKP+18} didn't propose a suitable numerical
method for solving the equations. Multi-fluids promises big improvements
in the representation of sub-grid-scale convection and unification
with the representation of turbulence, particularly at the grey zone.
However, there is a long way to go, particularly as multi-fluids requires
a dedicated model rather than being a stand alone parameterisation
for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
of the multi-fluid equations assuming two fluids that share the same
pressure (or that pressure differences are predominantly due to drag
between the fluids). \citeA{TEB19} showed that these equations (without
drag) are in fact unstable and can be stabilised by diffusion of vertical
velocity whereas \citeA{WM19} stabilised the equations with diffusion
and drag between fluids. Neither of these stabilisation techniques
are acceptable and in this paper we show that there are significant
and sustained pressure differences between the fluids (section \ref{sec:results}).

@@

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
over to the Boussinesq equations; convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Buossinesq equations. Therefore for simplicity we focus on the
multi-fluid Boussinesq equations without background stratification:
\begin{eqnarray}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\} \label{eq:sigma}\\
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i} & = & b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\} \label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt} & = & \alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}\\
\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i} & = & \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0\label{eq:divFree}\\
\sum_{i}\sigma_{i} & = & 1\label{eq:sumOne}
\end{eqnarray}
with variables defined in table \ref{tab:defns}.

\begin{table}[h]
\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
where $\rho^{\prime}$ are departures in density from a horizontally
uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
\end{tabular}

\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
\end{table}

@@

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=0$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=0$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=0$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.2\columnwidth}%
$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$%
\end{minipage} %
\begin{minipage}[t]{0.15\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline

@@

$\sigma_{1}$ & $b$, $b_{0}$ and $b_{1}$ & $w_{0}$ and $w_{1}$ & $P_{0}$ and $P_{1}$\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=1/2000\text{m}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage} }\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=0$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{01}=w_{1}0.2/r_{c}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0/2000\text{m}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=b_{i}$%
\end{minipage}}\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.15\columnwidth}%
$b_{ij}^{T}=0$%
\end{minipage} }\tabularnewline

@@

\multicolumn{4}{l}{%
\begin{minipage}[t]{0.17\columnwidth}%
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$%
\end{minipage}%
\begin{minipage}[t]{0.18\columnwidth}%
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$%
\end{minipage}%
\begin{minipage}[t]{0.24\columnwidth}%
$C_{D}/r_{c}=0$%
\end{minipage}%
\begin{minipage}[t]{0.25\columnwidth}%
$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$%
\end{minipage}}\tabularnewline

@@

The multi-fluid Boussinesq equations can have divergence in each fluid
while the divergence averaged over all fluids is zero. A model is
proposed and validated for the pressure difference between the rising
and falling fluids based on the divergence of each fluid. The use
of a different pressure for each fluid is not only realistic but also
leads to stable solutions of the multi-fluid equations.

@@

Single column multi-fluid modelling with moisture has already been
demonstrated by \citeA{TEB19}. Two important next steps are to simulate
convection in the grey zone (where it is partially resolved) and to
represent sub-grid-scale variability within each fluid by solving
multi-fluid prognostic equations for turbulent kinetic energy and
other moments of the sub-grid variability. These can be used to inform
cloud base mass flux (since only the most buoyant fluid will transfer
from the stable environment to the buoyant plume) and inform models
of the properties of the fluid that is transferred. This will lead
to a unified parameterisation of turbulence and convection and will
take multi-fluid modelling of convection beyond existing paradigms.

>>>>

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%
\addeditor{HW}

@@

Slow progress has been made improving the parameterisation of sub-grid-scale
convection since \citeA{AS74}, \citeA{Tied89}, \citeA{GR90} and \citeA{KF90}. Convection is still
one of the weakest aspects of large scale models of the atmosphere
\cite{HPB+14,SAB+13,ipcc41}. Improvements have been made \add[HW]{by} relaxing
the quasi-equilibrium assumption \cite{PR98,GG05,Par14}, including
stochasticity \cite{PC08} and allowing net mass transport by convection
\cite{KB08,MB19}. These developments have enabled limited simulation
in the grey zone, where convection is partially resolved. However
there are still systematic biases implying that improvements should
still be possible.

\citeA{TWV+18} proposed multi-fluid modelling of convection in order
to treat non-equilibrium and net mass transport correctly and consistently
with the same numerics and physics controlling thermals, the stable
environment and downdraught dynamics. \citeA{Yano14} derived similar
equations for multiple segments and showed how this is a generalisation
of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
diffusivity mass flux'' or extended EDMF scheme also uses similar
equations but \citeA{TKP+18}
\change[HW]{didn't propose a suitable numerical method for solving the equations.}
{only solve the equations in a single column without coupling to the continuity equation of a dynamical core.}
Multi-fluids promises big improvements
in the representation of sub-grid-scale convection and unification
with the representation of turbulence, particularly at the grey zone.
However, there is a long way to go, particularly as multi-fluids requires
a dedicated model rather than being a stand alone parameterisation
for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
of the multi-fluid equations assuming two fluids that share the same
pressure (or that pressure differences are predominantly due to drag
between the fluids). \citeA{TEB19} showed that these equations (without
drag) are in fact unstable and can be stabilised by diffusion of vertical
velocity whereas \citeA{WM19} stabilised the equations with diffusion
and drag between fluids. Neither of these stabilisation techniques
are acceptable and in this paper we show that there are significant
and sustained pressure differences between the fluids (section \ref{sec:results}).

@@

\begin{table}[ht]
\begin{tabular}{c>{\raggedright}p{0.85\textwidth}}
$\sigma_{i}$ & Volume fraction of fluid $i$ so that $\sum_{i}\sigma_{i}=1$\tabularnewline
$\mathbf{u}_{i}$ & Velocity of fluid $i$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$w_{i}$ & Vertical component of $\mathbf{u}_{i}$ ($\text{m}\text{s}^{-1}$)\tabularnewline
$S_{ij}$ & Transfer from fluid $i$ to $j$ ($\text{s}^{-1}$)\tabularnewline
$P_{i}$ & Non-hydrostatic pressure of fluid $i$ $=p^{\prime}/\rho_{r}$ ($\text{m}^{2}\text{s}^{-2}$)\tabularnewline
$\psi_{ij}^{T}$ & Value of variable $\psi$ transferred from fluid $i$ to $j$\tabularnewline
$b$ & Buoyancy defined as -$g\rho^{\prime}/\text{\ensuremath{\rho}}_{r}$
where $\rho^{\prime}$ are departures in density from a horizontally
uniform reference, $\rho_{r}$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$b_{i}$ & Buoyancy of fluid $i$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$D_{i}\big/Dt$ & Total derivative with respect to fluid $i$ $=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$\tabularnewline
$\mathbf{D}_{ij}$ & Drag on fluid $i$ from fluid $j$ ($\text{m}\text{s}^{-2}$)\tabularnewline
$\gamma$ & Coefficient for setting the pressure local for each fluid ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$C_{D}$ & Drag coefficient $=0$ or 1\tabularnewline
$r_{c}$ & Plume radius used for defining the drag between fluids (m)\tabularnewline
$\alpha$ & Diffusivity of buoyancy ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
$\nu$ & Viscosity ($\text{m}^{2}\text{s}^{-1}$)\tabularnewline
\end{tabular}
\caption{Definitions of variables for the multi-fluid Boussinesq equations.\label{tab:defns}}
\end{table}

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
over to the Boussinesq equations; convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Buossinesq equations. Therefore for simplicity we focus on the
\remove[HW]{multi-fluid} Boussinesq equations without background stratification:
\note[HW]{This is additional material until the start of 2.1}
\begin{eqnarray}
\frac{D\mathbf{u}}{Dt}+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
\label{eq:singleMom}
\\
\frac{Db}{Dt} & = & \alpha\nabla^{2}b
\label{eq:singleb}
\\
\nabla\cdot\mathbf{u} & = & 0
\label{eq:singleDivFree}
\end{eqnarray}
where variables are defined in table \ref{tab:defns}. 
These equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations. Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere and satisfy:
\begin{equation}
\frac{DI_i}{Dt}=0.
\label{eq:LagrangianLabel}
\end{equation}
Applying the conditional average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$:
\begin{eqnarray}
\sigma_i &=& \overline{I_i} \\
\sigma_i \mathbf{u}_i &=& \overline{I_i \mathbf{u}} \\
\sigma_i b_i &=& \overline{I_i b}
\label{eq:defineFluidFields}
\end{eqnarray}
which implies
\begin{equation}
\sum_{i}\sigma_{i}  =  1.
\label{eq:sumOne}
\end{equation}
As we are considering the Boussinesq equations we assume that variations in density only affect the buoyancy terms so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.

To derive a transport equation for $\sigma_i$ we combine (\ref{eq:LagrangianLabel}) with $I_i$ times (\ref{eq:singleDivFree}) and volume average. After permuting operators with the averaging \cite<as described by>{TWV+18} and using the definitions of $\sigma_i$ and $\mathbf{u}_i$ we get the evolution equation for $\sigma_i$:
\begin{equation}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i}  =  \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\}
\label{eq:sigma}
\end{equation}
which also includes transfers between fluids with $\sigma_{i}S_{ij}$ being the transfer from fluid $i$ to $j$.

Next we will consider conditionally averaging the terms of the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations. Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
\begin{eqnarray}
\overline{I_i \mathbf{u} \cdot \nabla \mathbf{u}} &=& \sigma_i \mathbf{u}_i \cdot \nabla \mathbf{u}_i + F_\text{SF}^{\mathbf{u}_i} \\
\overline{I_i \mathbf{u} \cdot \nabla b} &=& \sigma_i \mathbf{u}_i \cdot \nabla b_i + F_\text{SF}^{b_i}
\label{eq:filterAdvection}
\end{eqnarray}
The sub-filter-scale fluxes will be absorbed into the diffusion terms for momentum and buoyancy.

Since viscosity ($\nu$) and thermal diffusivity ($\alpha$) are constant, conditional averaging of the diffusion terms is straightforward:
\begin{eqnarray}
\overline{I_i \nabla \cdot \nu \nabla \mathbf{u}} &=& \sigma_i \nabla\cdot\bigl(\nu \nabla\mathbf{u}_i \bigr) \\
\overline{I_i \nabla \cdot \alpha \nabla b} &=& \sigma_i \nabla\cdot\bigl(\alpha \nabla b_i \bigr).
\end{eqnarray}

Unlike \citeA{TWV+18} we define separate pressures for each fluid, $P_i$. The pressures are defined to satisfy:
\begin{equation}
\sigma_i \nabla P_i = \overline{I_i \nabla P}.
\end{equation}
Combining these gives the conditionally averaged momentum and buoyancy equations:
\begin{eqnarray}
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i}
& = &
b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\}
\label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt}
& = &
\alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}
\end{eqnarray}
where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$, $\mathbf{u}_{ij}^T$ is the velocity of the fluid transferred from $i$ to $j$, $b_{ij}^T$ is the buoyancy of the fluid transferred from $i$ to $j$ and $\mathbf{D}_{ij}$ is the drag of fluid $j$ on fluid $i$. It is not clear that drag between fluids is appropriate for this form of the equations but it is commonly used in multi-phase modelling \cite<eg>{?} so we will investigate sensitivity to drag in section \ref{sec:results}.

Finally the multi-fluid version incompressibility is
\begin{equation}
\sum_{i}\nabla\cdot\sigma_{i}\mathbf{u}_{i}  = \nabla\cdot\sum_{i}\sigma_{i}\mathbf{u}_{i}=0.
\label{eq:divFree}
\end{equation}

@@

\setlength{\tabcolsep}{2pt}

@@

\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=0$, \hspace{6pt}
$\gamma=0$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}} \tabularnewline 

@@

\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=0$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=2.3\!\!\times\!\!10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline

@@

$\sigma_{1}$ ($\text{m}^3/\text{m}^3$) & $b$ and $b_{i}$ ($\text{m}\text{s}^{-2}$) & $w_{0}$ and $w_{1}$ (m/s) & $P_{0}$ and $P_{1}$ ($\text{m}^2 \text{s}^{-2}$)\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=1/2000\text{m}^{-1}$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
} }\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=0$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
$S_{01}=w_{1}0.2/r_{c}$, \hspace{4pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{4pt}
$C_{D}/r_{c}=0/2000\text{m}^{-1}$, \hspace{4pt}
$b_{ij}^{T}=b_{i}$.
}}\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.7\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=0$.
} }\tabularnewline

@@

\multicolumn{4}{c}{\framebox[0.8\linewidth]{\centering
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, \hspace{6pt}
$\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$, \hspace{6pt}
$C_{D}/r_{c}=0$, \hspace{6pt}
$b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$.
}}\tabularnewline

@@

The multi-fluid Boussinesq equations can have divergence in each fluid
while the divergence averaged over all fluids is 
\change[HW]{zero}
{constrained to be zero following the single-fluid Boussinesq equations.}
A model is proposed and validated for the pressure difference between the rising
and falling fluids based on the divergence of each fluid. The use
of a different pressure for each fluid is not only realistic but also
leads to stable solutions of the multi-fluid equations.

@@

Single column multi-fluid modelling with moisture has already been
demonstrated by \citeA{TEB19} 
\add[HW]{and two dimensional simulations of the multi-fluid Euler equations by \protect\citeA{WM19} }.
Two important next steps are to simulate
convection in the grey zone (where it is partially resolved) and to
represent sub-grid-scale variability within each fluid by solving
multi-fluid prognostic equations for turbulent kinetic energy and
other moments of the sub-grid variability. These can be used to inform
cloud base mass flux (since only the most buoyant fluid will transfer
from the stable environment to the buoyant plume) and inform models
of the properties of the fluid that is transferred. This will lead
to a unified parameterisation of turbulence and convection and will
take multi-fluid modelling of convection beyond existing paradigms.
